---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ncbitaxids

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of ncbitaxids is to provide a simple interface for accessing complete lists of ncbi taxids belonging to important groups - such as bacteria, fungi, viruses, etc

## Installation

You can install the ncbitaxids from [GitHub](https://github.com/selkamand/ncbitaxids) with:

``` r
# install.packages("devtools")
devtools::install_github("selkamand/ncbitaxids")
```
## Example

To get a list of available taxid lists, run:

```{r available taxid lists}
library(ncbitaxids)

taxids_available_lists()
```

To load one of these lists, run `taxids_load_list("name_of_taxid_list")` again but with one of the available taxid lists specified

```{r load taxid list, eval=FALSE, echo=T, results='hide'}
taxids_load_list("all_bacterial_taxids.05_05_2022")
```


# Data source

Data was downloaded by navigating to the [NCBI taxonomy browser](https://www.ncbi.nlm.nih.gov/Taxonomy/Browser/wwwtax.cgi?mode=Info&id=2&lvl=3&lin=f&keep=1&srchmode=1&unlock) for major groups such as bacteria. Then selecting subtree links and sending the results to file in `taxid list` format.

To add more taxid sets, write newline separated taxids to a file called `<group_taxids_belong_to.date.txt>`.
Make sure taxid file is in inst/taxid_lists and the scripts of this package should automatically find it
